Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-24 submission5/core.tex
MPI-SP branding policy
Updated test runs

\begin{table}[]
\centering
\begin{tabular}{c|c|c|c}
  Bug & Property Violated & MTTF (s) & Tests \\
  \hline
      {\em LOAD\_NO\_CHECK\_DI}  & Confidentiality & 24.2 & 13.3 \\
      {\em STORE\_NO\_CHECK} & Integrity & 26.9 & 26 \\
      {\em HEADER\_NO\_INIT} & Integrity & 69.5 & 76.3 \\
  \hline
  \hline
      {\em PER\_DEPTH\_TAG} & Integrity & 189.7 & 8342.5  \\
      {\em LOAD\_NO\_CHECK\_LT}  & Integrity & 23.5 & 12.0 \\
      {\em LOAD\_NO\_CHECK\_LT}  & Confidentiality & 19.2 & 695.5 \\
      {\em STORE\_NO\_UPDATE} & Integrity & 70 & 80.6  \\
      {\em STORE\_NO\_UPDATE} & Confidentiality & 4.9 & 88.5 \\
  \hline
\end{tabular}
\vspace*{1em}
\caption{MTTF for finding bugs in erroneous micro-policies: DI (top) and LTC (bottom)}
\vspace*{-2em}
\label{tab:bug-table}
\end{table}

>>>>

\begin{table}[]
\centering
\begin{tabular}{c|c|c|c}
  Bug & Property Violated & Ave. MTTF (s) & Tests \\
  \hline
      {\em LOAD\_NO\_CHECK}  & Confidentiality & 24.2 & 13.3 \\
      {\em STORE\_NO\_CHECK} & Integrity & 26.9 & 26 \\
      {\em HEADER\_NO\_INIT} & Integrity & 69.5 & 76.3 \\
  \hline
  \hline
      {\em PER\_DEPTH\_TAG} & Integrity & 10.5 & 82 \\
      {\em PER\_DEPTH\_TAG} & Confidentiality & 16.85 & 88 \\
      {\em LOAD\_NO\_CHECK}  & Integrity & 8.82 & 34.3 \\
      {\em LOAD\_NO\_CHECK}  & Confidentiality & 22.55 & 127 \\
      {\em STORE\_NO\_UPDATE} & Integrity & 6.96 & 101 \\
      {\em STORE\_NO\_UPDATE} & Confidentiality & 17.34 & 11 \\
  \hline
\end{tabular}
\vspace*{1em}
\caption{MTTF for finding bugs in erroneous micro-policies: DI (top) and LTC (bottom)}
\vspace*{-2em}
\label{tab:bug-table}
\end{table}
